---
title: "Case Study 5"
author: "Brink"
date: "9/22/2022"
output: 
  html_document:
    theme: united
    keep_md: True
    code_folding: 'hide'
---

```{r}
library(tidyverse)
library(downloader)
library(readxl)
```
Explaining the article: The interactive, malleable set of data allowed the user to break down different data groups and compare them to the total of all gun deaths. It was extremely effective in showing the scale of gun deaths in our country and how desparately we need solutions to these problems. One thing that was particularly shocking was the notion that 2/3 of all deaths were suicides. 

```{r}
GunData <- tempfile()
download("https://raw.githubusercontent.com/fivethirtyeight/guns-data/master/full_data.csv", GunData, mode = "wb")
gunData <- read_csv(GunData)
gunData_new <- gunData %>%
  filter(age != "", intent != "")
str(gunData)
```

```{r}
gunsData <- gunData_new %>%
  mutate(agegroup =
          case_when(
            age >= 0 & age <= 14 ~ "under 15",
            age >= 15 & age <= 34 ~ "15-34",
            age >= 35 & age <= 64 ~ "35-64",
            age >= 65 ~ "65+"),
         agegroup = fct_relevel(agegroup, 
            "under 15", "15-34", "35-64", 
            "65+"))
```

```{r}
ggplot(data = gunsData, aes(x = agegroup, fill = sex)) +
  geom_bar() +
  facet_wrap(~intent, nrow = 2, scales = 'free') +
  scale_fill_manual(values = c('#FD6D6D', '#5A84D3')) +
  ggtitle("Gun deaths for different age groups") +
  theme_bw()
```

```{r}
ggplot(data = gunData_new, aes(x = age, fill = intent)) +
  geom_density(position = 'fill', alpha = .6) +
  facet_wrap(~sex) +
  scale_fill_manual(values = c("#8CDBAA","#FFA727","lightslateblue","hotpink")) +
  ggtitle("Male vs Female Gun Death Rates") +
  theme_bw()
```

```{r}
season <- gunData_new %>%
  filter(education != "") %>%
  mutate(seasons = as.factor(fct_collapse(month,
          "Spring" = c("03", "04", "05"),
          "Summer" = c("06", "07", "08"),
          "Fall" = c("09", "10", "11"),
          "Winter" = c("12", "01", "02"))),
         seasons = fct_relevel(seasons, 
            "Spring", "Summer", "Fall", 
            "Winter")
  )
```

```{r}
ggplot(season, aes(intent, fill = education)) +
  geom_bar() +
  facet_wrap(~seasons, scales = "free") +
  ggtitle("Education level across different seasons") +
  theme_bw()
```

```{r}
ggplot(season, aes(seasons, fill = race)) +
  geom_bar() +
  facet_wrap(~race, scales = 'free') +
  ggtitle("Gun deaths considering race and season") +
  theme_bw() +
  theme(legend.position = 'none')
```

