---
title: "Task 20(animation of Case 9)"
author: "Brink"
date: "11/16/2022"
output: 
  html_document:
    keep_md: TRUE
editor_options: 
  chunk_output_type: console
---

```{r}
library(ggplot2)
library(readr)
library(knitr)
library(tidyverse)
library(dplyr)
library(forcats)
library(downloader)
library(corrplot)
library(tidyquant)
library(timetk)
library(dygraphs)
library(scales)
library(leaflet)
```

```{r}
tickers_today <- tq_get(c("CXW", "F", "GM", "JCP", "KR", "WDC", "NKE","T", "WDAY", "WFC", "WMT"), get = "stock.prices", from = today()-years(5), to = today())
head(tickers_today)
```
Graph setup
```{r}
setup <- tickers_today %>%
  select(symbol, date, adjusted) %>%
  pivot_wider(names_from = symbol, values_from = adjusted) %>%
  tk_xts(date_var = date)

dygraph(setup, main = "Ticker Chart") %>%
  dyRebase(percent = TRUE) %>%
  dyShading(from = today()-years(5), to = today()) %>%
  dyRangeSelector()
```
2nd dy Chart
```{r}
monthlyReturns <- tickers_today %>%
  group_by(symbol) %>%
  tq_transmute(adjusted, mutate_fun = monthlyReturn) %>%
  select(symbol, date, monthly.returns) %>%
  pivot_wider(names_from = symbol, values_from = monthly.returns) %>%
  tk_xts(date_var = date)
monthlyReturns

dygraph(monthlyReturns, main = "Stock Comparison Monthly Returns") %>%
  dyOptions(colors = RColorBrewer::brewer.pal(3, "Set2"))
```

GGPlot Visualization (Volume Chart)
```{r}
volume <- tickers_today %>%
  select(symbol, date, volume)
head(volume)

volumechart <- ggplot(data = volume, mapping = aes(x = date, y = volume, color = symbol)) +
  geom_line() +
  scale_y_continuous(labels = comma) +
  facet_wrap(~symbol)
volumechart
```
After reading in the data, I first had to create a dataframe (setup) in order to convert the tickers we were given into XTS in order to graph them using a time series plot through dygraph. The dyrebase and dyshading were added to set a base value percentage for the chart to refer to as it shows the data from the last 5 years. While creating an additional plot using dygraphs, I referred to the Day17TidyquantTimeTK class code to build a plot that didn't refer from the last 5 years, but compared the respective stock with it's performance in the previous year. The most notable aspect to the volume chart is that I felt it essential to convert the yaxis into digestable numbers because as an average observer you can't really put the chart results into perspective until you see those full values. 

Section 2 (My Stocks)
```{r}
MyStocks <- tq_get(c("QQQ","MO","KO","ABB","LH","CINF"), get = "stock.prices", from = today()-years(5), to = today())
```

Setup for first DY
```{r}
newsetup <- MyStocks %>%
  select(symbol, date, adjusted) %>%
  pivot_wider(names_from = symbol, values_from = adjusted) %>%
  tk_xts(date_var = date)

dygraph(newsetup, main = "Ticker Chart") %>%
  dyRebase(percent = TRUE) %>%
  dyShading(from = today()-years(5), to = today()) %>%
  dyRangeSelector()
```

Setup for second DY
```{r}
monthlyReturns <- MyStocks %>%
  group_by(symbol) %>%
  tq_transmute(adjusted, mutate_fun = monthlyReturn) %>%
  select(symbol, date, monthly.returns) %>%
  pivot_wider(names_from = symbol, values_from = monthly.returns) %>%
  tk_xts(date_var = date)
monthlyReturns

dygraph(monthlyReturns, main = "Stock Comparison Monthly Returns") %>%
  dyOptions(colors = RColorBrewer::brewer.pal(3, "Set2"))
```

```{r}
library(gganimate)
library(gifski)
```

Setup for GGplot volume
```{r}
volume <- MyStocks %>%
  select(symbol, date, volume)
head(volume)

volumechart <- ggplot(data = volume, mapping = aes(x = date, y = volume, color = symbol)) +
  geom_line() +
  facet_wrap(~symbol)
volumechart
```

```{r}
library(viridis)
```


```{r}
ggplot(data = volume, mapping = aes(x=date, y=volume, group=symbol, color=symbol)) +
  geom_line()+
  geom_point()+
  scale_color_viridis(discrete = TRUE) +
  ggtitle("Wow")+
  theme_bw()+
  labs(title = "date: {frame_along}")  +
  transition_reveal(date)
```

