---
title: "Case Study 4"
author: "Brink"
date: "9/19/2022"
output: 
  html_document:
    keep_md: TRUE
    code_folding: 'hide'
---

```{r}
library(nycflights13)
library(tidyverse)
library(lubridate)
library(ggrepel)
library(ggplot2)
library(readr)
library(knitr)
library(dplyr)
library(forcats)
library(downloader)
```

```{r}
?flights
str(flights)
head(flights)
```
Question 1. If I am leaving before noon, which two airlines do you recommend at each airport (JFK, LGA, EWR) that will havethe lowest delay time at the 75th percentile?

When approaching this question, I knew that I had to make a ggplot for all of EWR, JFK, and LGA. The code between these are similar, with simply keeping the x as carrier and y as arrival delay, it was clear to see that OO and HA were the most efficent airlines.

```{r}
EWRdata <- filter(flights, origin == "EWR")
head(EWRdata)
```

```{r}
EWRplot <- ggplot(data = EWRdata, mapping = aes(x = carrier, y = arr_delay, size = arr_delay, color = carrier)) +
  geom_point()+
  labs(x = "Carriers",
       y = "Arrival Delay",
       title = "Airlines with lowest arrival time at EWR",
       subtitle = "Skywest Arilines INc. & Alaska Airlines Inc. have lowest arrival delay") +
  theme_bw()
EWRplot
```

```{r}
JFKdata <- filter(flights, origin == "JFK")
head(JFKdata)
```

```{r}
JFKplot <- ggplot(data = JFKdata, mapping = aes(x = carrier, y = arr_delay, size = arr_delay, color = carrier)) +
  geom_point() +
  labs(x = "Carriers",
       y = "Arrival Delay",
       title = "Airlines with lowest arrival time at JFK",
       subtitle = "Hawaiian Arilines Inc. & US Airways Inc. have lowest arrival delay") +
  theme_bw()
JFKplot
```

```{r}
LGAdata <- filter(flights, origin == "LGA")
head(LGAdata)
```

```{r}
LGAplot <- ggplot(data = LGAdata, mapping = aes(x = carrier, y = arr_delay, size = arr_delay, color = carrier)) +
  geom_point() +
  labs(x = "Carriers",
       y = "Arrival Delays",
       title = "Airlines with lowest arrival time at LGA",
       subtitle = "Skyest Airlines Inc. & Endeavor Air Inc. have lowest arrival delay") +
  theme_bw()
LGAplot
```
Which origin airport is best to minimize my chances of a late arrival when I am using Delta Airlines?

EWR is the the best airport to fly with Delta as it has the lowest amount of arrival delays.
```{r Question 2}
Delta <- filter(flights, carrier == "DL", )
ggplot(Delta, aes(x = origin, y = arr_delay))+
  geom_count()+
    theme(axis.text.x=element_text(angle=90, hjust=1))
```

Question 3: Which destination airport is the worst airport for arrival time?

Keep same ggplot code, except swap X for origin.
```{r}
WorstAirline <- ggplot(data = flights, mapping = aes(x = origin, y = arr_delay, color = origin, size = arr_delay)) +
  geom_point() +
  labs(x = "Origin Airport", 
       y = "Arrival Delay",
       title = "Airports with the worst arrival time",
       subtitle = "JFK is the worst location to fly with",
       caption = "High density of points") +
  theme_bw()
WorstAirline
```

